Topological Equivariant Artist Model

### 2021-03-15 paper/paper.tex
rewrote channels to remove words

\usepackage{microtype}                 % use micro-typography (slightly more compact, better to read)
\PassOptionsToPackage{warn}{textcomp}  % to address font issues with \textrightarrow
\usepackage{textcomp}                  % use better special symbols
\usepackage{mathptmx}                  % use matching math font
\usepackage{times}                     % we use Times as the main font
\renewcommand*\ttdefault{txtt}         % a nicer typewriter font
\usepackage{cite}                      % needed to automatically sort the references
\usepackage{tabu}                      % only used for the table example
\usepackage{booktabs}                  % only used for the table example
%% We encourage the use of mathptmx for consistent usage of times font
%% throughout the proceedings. However, if you encounter conflicts
%% with other math-related packages, you may want to disable it.
\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{mathrsfs} % math script fonts
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\usepackage{minted}
\setminted[python]{fontsize=\scriptsize, 
                   linenos,
                   numbersep=8pt,
                   autogobble, 
                   frame=lines,
                   bgcolor=bg,
                   framesep=3mm} 
\usepackage{notation} % move this later
%% In preprint mode you may define your own headline. If not, the default IEEE copyright message will appear in preprint mode.
%\preprinttext{To appear in IEEE Transactions on Visualization and Computer Graphics.}

@@

One example of an equivariant \vchannel\ is illustrated in \autoref{fig:math:artist:nu}, which is a mapping from \textbf{Strings} to symbols. The data is an example of a Steven's nominal measurement set, which is defined as having on it permutation group actions 
\begin{equation*}
  \text{ if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)
\end{equation*}
such that shuffling the words must have an equivalent shuffle of the symbols they are mapped to. This is illustrated in the identical actions, represented by the colored arrows, on the words and emojis. To preserve ordinal and partial order monoid actions, \vchannel\ must be a monotonic function such that given $\delement_1, \delement_2 \in \dtotal_{i}$,
\begin{equation*}
\text{ if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2*)
\end{equation*}
the visual encodings must also have some sort of ordering. For interval scale data, \vchannel\ is equivariant under translation monoid actions if 
\begin{equation*}
\vchannel (x + c) = \vchannel(x) + c
\end{equation*}
while for ratio data, there must be equivalent scaling\cite{weissteinSimilarityTransformation} 
\begin{equation*}
\vchannel(xc) = \vchannel(x)*c 
\end{equation*}
We therefore can test if a \vchannel\ is equivariant by testing the actions under which it must  commute. For example, given a a transform $\vchannel_{i}(x) = .5$ on interval data, it must commute under translation. Testing this constraint with a translation action $t(x) = x+2$
\begin{align*}
  \vchannel(t(\delement + 2)) & \overset{?}{=} \vchannel(\delement) + 2\\
  .5 &\neq .5 + 2
\end{align*}
\vchannel\ does not commute and is therefore invalid. The constraints on \vchannel\ can be embedded into the artist such that the \vchannel\ functions can test for equivariance and also provide guidance on constructing new \vchannel\ functions.

>>>>

\usepackage{microtype}                 % use micro-typography (slightly more compact, better to read)
\PassOptionsToPackage{warn}{textcomp}  % to address font issues with \textrightarrow
\usepackage{textcomp}                  % use better special symbols
\usepackage{mathptmx}                  % use matching math font
\usepackage{times}                     % we use Times as the main font
\renewcommand*\ttdefault{txtt}         % a nicer typewriter font
\usepackage{cite}                      % needed to automatically sort the references
\usepackage{tabu}                      % only used for the table example
\usepackage{booktabs}                  % only used for the table example
%% We encourage the use of mathptmx for consistent usage of times font
%% throughout the proceedings. However, if you encounter conflicts
%% with other math-related packages, you may want to disable it.
\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{mathrsfs} % math script fonts
\usepackage{tabulary}
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\usepackage{minted}
\setminted[python]{fontsize=\scriptsize, 
                   linenos,
                   numbersep=8pt,
                   autogobble, 
                   frame=lines,
                   bgcolor=bg,
                   framesep=3mm} 
\usepackage{notation} % move this later
%% In preprint mode you may define your own headline. If not, the default IEEE copyright message will appear in preprint mode.
%\preprinttext{To appear in IEEE Transactions on Visualization and Computer Graphics.}

@@

The equivariant \vchannel\ illustrated in \autoref{fig:math:artist:nu} is a mapping from \textbf{Strings} to symbols, which is an example of a Steven's nominal measurement. More generally, for the Steven's scales an equivariant \vchannel\ has the following properties
\begin{table}[H]
  \begin{tabulary}{\columnwidth}{llL}
      nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
      ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
      interval &  translation &  $\vchannel (x + c) = \vchannel(x) + c$ \\
      ratio &  scaling &  $\vchannel(xc) = \vchannel(x)*c $\\
  \end{tabulary}
\end{table}
\noindent where the middle column is the group structure. We therefore can test if a \vchannel\ is equivariant by testing the actions under which it must  commute. For example, given a a transform $\vchannel_{i}(x) = .5$ on interval data, it must commute under translation. Testing this constraint with a translation action $t(x) = x+2$
\begin{align*}
  \vchannel(t(\delement + 2)) & \overset{?}{=} \vchannel(\delement) + 2\\
  .5 &\neq .5 + 2
\end{align*}
\vchannel\ does not commute and is therefore invalid. The constraints on \vchannel\ can be embedded into the artist such that the \vchannel\ functions can test for equivariance and also provide guidance on constructing new \vchannel\ functions.
